% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

\documentclass[12pt,letterpaper,openany]{memoir}

% This is how you get rid of a (possible) blank page between
% frontmatter and main matter. See [1].
% [1]: http://tex.stackexchange.com/questions/153650/memoir-class-forces-recto-page-after-mainmatter
\usepackage{etoolbox}
\makeatletter
\patchcmd{\@smemmain}{\cleardoublepage}{\clearpage}{}{}
\patchcmd{\@smemmain}{\cleardoublepage}{\clearpage}{}{}
\makeatother

% Not double space, not single, but inbetween
\OnehalfSpacing

% 1in margins everywhere. The tricky part is that the "upper margin"
% refers to where the *text* starts, not the header, so you need to
% give some extra space for the header. Probably some way to
% explicitly set the distance to the header, but this is simple and
% close enough.

\setlrmarginsandblock{1.0in}{1.0in}{*}
\setulmarginsandblock{1.45in}{1.0in}{*}
\checkandfixthelayout

% See memoir manaul for this stye. It put page numbers in the footer.
% The header has chapter/section name and a ruled line.
\copypagestyle{my-ruled}{ruled}
  \makeevenfoot{my-ruled}{}{\thepage}{}
  \makeoddfoot{my-ruled}{}{\thepage}{}

\pagestyle{my-ruled}


\usepackage{thesis}

% show labels in printed document. Remove for ``real'' typesetting
%\usepackage{showkeys}

% number equations, tables, and figures by chapter
\numberwithin{equation}{chapter}
\numberwithin{figure}{chapter}
\numberwithin{table}{chapter}

% Bibliography
% For more bibliography format stuff, see http://www.khirevich.com/latex/biblatex/
\usepackage[
    backend=biber,
    style=numeric-comp,
    sorting=none,
    url=false,
    maxbibnames=100
    ]{biblatex}
\addbibresource{thesis.bib}

%%% BEGIN DOCUMENT
\begin{document}

\frontmatter

% Title page. All this code (and the signature page code) was copied
% from the "official" CU latex template [1].
% [1]: http://www.colorado.edu/oit/sites/default/files/thesis.cls

\newcommand{\thesistitle}{Submillimeter Video Imaging with a Superconducting Bolometer Array}

\thispagestyle{empty}
\vspace*{\fill}
\begin{center}
  \parbox{6.0in}{
    \begin{center}
      \DoubleSpacing
      \MakeUppercase{\thesistitle} \\
      by \\
      DANIEL THOMAS BECKER \\
      B.S., Rice University, 1994 \\
      M.S., University of Colorado, 2009
    \end{center}
  }
\end{center}
\vspace*{1in}
\begin{center}
  \DoubleSpacing
  A dissertation submitted to the\\
  Faculty of the Graduate School of the\\
  University of Colorado in partial fulfillment\\
  of the requirements for the degree of\\
  Doctor of Philosophy \\
  Department of Physics \\
  2014
\end{center}
\vspace*{\fill}
\newpage

% Signature page

\thispagestyle{empty}
\vspace*{\fill}
\begin{center}
  \SingleSpacing
  This dissertation entitled:\\
  \thesistitle{} \\
  written by Daniel Thomas Becker \\
  has been approved for the Department of Physics \\
\end{center}

\vspace*{2mm}

\begin{center}
  \normalsize
  \vspace*{16mm}
  \vrule width 80mm height 0.2mm\\
  Nils Halverson
\end{center}

\begin{center}
  \normalsize
  \vspace*{16mm}
  \vrule width 80mm height 0.2mm\\
  Kent Irwin
\end{center}

\vspace*{9mm}

\begin{flushright}
  Date~{\vrule width 55mm height 0.2mm}
\end{flushright}

\vspace*{\fill}
\begin{center}
  \SingleSpacing
  \parbox{4.50in}{
  The final copy of this dissertation has been examined by
  the signatories, and we find that both the content
  and the form meet acceptable presentation standards
  of scholarly work in the above mentioned discipline.}
\end{center}
\vspace*{\fill}
\newpage

% Now the abstract, in CU's format


\begin{flushleft}
Becker, Daniel Thomas (Ph.D., Physics)

\thesistitle

Dissertation directed by Associate Professor Nils Halverson
\end{flushleft}

\vspace*{0.7cm}

% use siunitx
Millimeter wavelength radiation holds promise for detection of security threats at a distance, including suicide bombers and maritime threats in poor weather.
The high sensitivity of superconducting Transition Edge Sensor (TES) bolometers makes them ideal for passive imaging of thermal signals at millimeter and submillimeter wavelengths.

I have built a 350 GHz video-rate imaging system using an array of feedhorn-coupled TES bolometers.
The system operates at standoff distances of 16 m to 28 m with a measured spatial resolution of 1.4 cm (at 17 m).
It currently contains one 251-detector sub-array, and can be expanded to contain four sub-arrays for a total of 1004 detectors.
The system has been used to take video images that reveal the presence of weapons concealed beneath a shirt in an indoor setting.

This dissertation describes the design, implementation and characterization of this system.
It presents an overview of the challenges associated with standoff passive imaging and how these problems can be overcome through the use of large-format TES bolometer arrays.
I describe the design of the system and cover the results of detector and optical characterization.
I explain the procedure used to generate video images using the system, and present a noise analysis of those images.
This analysis indicates that the Noise Equivalent Temperature Difference (NETD) of the video images is currently limited by artifacts of the scanning process.
More sophisticated image processing algorithms can eliminate these artifacts and reduce the NETD to 100 mK, which is the target value for the most demanding passive imaging scenarios.
I finish with an overview of future directions for this system.
%%%(264 words, 350 allowed)

\newpage
\begin{flushleft}\textbf{\Huge Acknowledgements}\end{flushleft}
\vspace{0.25in}

It is a truth universally acknowledged that a graduate student in possession of a draft dissertation must be in want of an editor.
I thank Nils Halverson, Bill Becker, and Linda Becker for carefully reading this dissertation and providing much useful feedback and advice.
Any remaining grammatical, spelling, or other errors are entirely my own.

I had help from many different people while performing the work described in this dissertation.
At some point in time, everyone associated with NIST's Quantum Sensors Project provided either useful advice as I worked through the design process, or gave concrete help in the lab.
The sections at the ends of Chapters 4 and 5 give the names of people who were particularly helpful with specific areas.
I would also like to thank Mike Niemack, who explained to me how to use the \MCE\ as well as giving useful advice regarding the design and testing of the detectors.
Conversations with Doug Bennett have been helpful in understanding \TES\ detectors in general.
Hannes Hubmayr was a useful resource for \TES\ detectors and submillimeter detection.
Randy Doriese helped me to understand \SQUID\ readout.
Carl Reintsema designed circuit boards for reading out the prototype detectors, and came up with the idea of reading out the mirror position using the \SQUID\ readout system.
Colin Fitzgerald, Jon Gard, Cale Gentry, and Bob Schwall all helped mount and unmount the cryostat from the primary mirror, a time-consuming and unpleasant task.

Of course none of this work would be possible without good advisors, and I thank Nils Halverson for giving me an initial opportunity to work in the field of submillimeter detection, and Kent Irwin for the opportunity to continue working in the field.
Both Nils and Kent have been very supportive of me, particularly in light of the challenges I have faced as a graduate student attempting to support a family with young children, and I deeply appreciate their support and help.

I am blessed with a supportive family and extended family. I particularly thank my parents for, well, everything, and my sister Kate for serving as an inspiration in many different ways.
During the months of writing this dissertation my children have had to put up with a father spending too much time writing in the basement, and I thank them for their patience with me.
Finally, and most importantly, I thank my wife, Terzah, who helped in many small as well as large ways, and without whose love and support none of this would be possible.

\newpage

\tableofcontents* % the asterisk means that the contents itself isn't put into the ToC

\newpage
\listoftables

\newpage
\listoffigures

\mainmatter

\include{ch1-intro}

\include{ch2-specs}

\include{ch3-tes-theory}

\include{ch4-sys-design}

\include{ch5-det-design}

\include{ch6-subarray}

\include{ch7-imaging}

\include{ch8-summary}

% Now the bibliography. It should be single-spaced.
\SingleSpacing
\printbibliography

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
